### 2024-09-25 manuscript.tex
Section on LTS results

Fig. \ref{fig:cyclone-stability}b shows a geographical distribution of the LTS.

>>>>

Fig. \ref{fig:cyclone-stability}b shows a geographical distribution of
relatively stable and unstable conditions as determined by the LTS.  The
relatively unstable conditions are prevalent in the mid SO (50--65°S), which
might be explained by the relatively cold near-surface air overlying relatively
warm sea surface. Relatively stable conditions are prevalent elsewhere over the
SO. The distribution is also less zonally symmetric than the cyclonic activity.
In the high-latitude SO, the presence of sea ice might have significant
stabilising effect. The ERA5 renalysis is also substantially more stable than
ICON across the whole region.
